Hydras \& Co.

### 2022-03-02 doc/part-hydras.tex
minor corrections

@@

@@

>>>>

\subsection{About Gaia}
Chapter~\vref{gaia-chapter} describes the present state of a
project of making compatible the libraries \HydrasLib and \gaia. At present, both libraries contain a version of the inductive type \texttt{T1}, with the same base name for the constructors.

\inputsnippets{nfwfgaia/T1def}

Thus, many examples of this and following chapters can be run
in \gaia's context. We will signal any difference (notation, name) which may appear.
 A closer integration (same data type and functions) is still in project.

@@

\begin{gaiacompat}

  In \texttt{gaia.ssete9}, the $n$-th finite ordinal is written
  \texttt{$\backslash${F}\,$n$}. There is no coercion in \gaia from \texttt{nat} to finite ordinals.

  From~\href{../theories/html/gaia_hydras.HydraGaia_Examples.html}{gaia\_hydras.HydraGaia\_Examples}.

  \inputsnippets{HydraGaia_Examples/Demoa}

\end{gaiacompat}

@@

\inputsnippets{T2/T2Def, T2/psiDef}
